---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CryptocurrencyEDAr

<!-- badges: start -->
[![R-CMD-check](https://github.com/UBC-MDS/CryptocurrencyEDAr/workflows/R-CMD-check/badge.svg)](https://github.com/UBC-MDS/CryptocurrencyEDAr/actions)
[![Codecov test coverage](https://codecov.io/gh/UBC-MDS/CryptocurrencyEDAr/branch/main/graph/badge.svg)](https://codecov.io/gh/UBC-MDS/CryptocurrencyEDAr?branch=main)
[![R build status](https://github.com/UBC-MDS/CryptocurrencyEDAr/workflows/R-CMD-check/badge.svg)](https://github.com/UBC-MDS/CryptocurrencyEDAr/actions)
[![codecov](https://github.com/UBC-MDS/CryptocurrencyEDAr/branch/master/graph/badge.svg)](https://app.codecov.io/gh/UBC-MDS/CryptocurrencyEDA)
<!-- badges: end -->

This is a R package to analyze historical cryptocurrency prices and performance through simple exploratory data analysis including calculations and plotting. Data is sourced from the KuCoin API. There are four functions that are included in this R package which are described in more detail below. Cryptocurrency investors and enthusiasts can use this package to analyze cryptocurrencies of interest.

There are existing R packages that support users to access information of cryptocurrency such as `crypto`, `crypto2` and `coinmarketcapr`. Among these 3 packages, only `coinmarketcapr` provides visualization of top currency. Indeed , there is no integrated R package for retrieving, analyzing, and visualizing cryptocurrency data altogether. Therefore, we want to build a simple tool that can facilitate simple cryptocurrency data analysis all at once.


## Function list

The package contains the following four functions:

- `retrieve_data`: downloads historical data using an an http request from a cryptocurrency exchange.

- `plot_price`: generates and visualizes a plot of the price of the cryptocurrenty inputted over a period of time.

- `daily_growth_rate`: performs calculation of daily growth rate of the price of the cryptocurrency inputted over a period of time.

- `avg_daily_return`: performs calculation of the average daily return of the inputted cryptocurrency price.


## Installation

You can install the development version of `CryptocurrencyEDAr` from
[GitHub](https://github.com/) with:

``` {r, results = "hide"}
# install.packages("devtools", quiet = TRUE)
devtools::install_github("UBC-MDS/CryptocurrencyEDAr")
```

## Usage
After installation, firstly load the functions from the package:
```{r}
devtools::load_all()
```

Now the functions are ready to use as follows:
```{r fig.width=6, fig.height=4}
price_df <- retrieve_data("BTC-USDT", "1day", "2021-01-01", "2021-12-31")
plot_price(df = price_df)
new_price_df <- daily_growth_rate(price_df, "Close")
head(new_price_df)
avg_daily_return(price_df$Close)
```

## Documentation

- Vignette homepage
- Introduction to CryptocurrencyEDAr package

## Contributors

We welcome and recognize all contributions. The following are current contributors. You can also see the list [here](DESCRIPTION). If you are interested in contributing to this project, please check out our CODE_OF_CONDUCT.md

- Berkay Bulut
- Cici Du
- Alex Yinan Guo
- Nobby Nguyen

## License

`CryptocurrencyEDAr` was created by MDS Students from Group-11 for course 524. It is licensed under the terms of the MIT license.

## Code of Conduct
  
  Please note that the CryptocurrencyEDAr project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
