---
title: "Introduction to CryptocurrencyEDAr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CryptocurrencyEDAr-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CryptocurrencyEDAr)
```

## Brief Introduction
CryptocurrencyEDAr is used for simple exploratory data analysis of historical cryptocurrency prices and performance.There are four functions that are included in this R package which are described in more detail below.
Cryptocurrency investors and enthusiasts can use this package to analyze cryptocurrencies of interest.

## Data
Data is sourced from the KuCoin API.  

## Function Demonstration

### Retrieve Data and Store it as a dataframe
This function downloads historical data using an an http request from a cryptocurrency exchange. It returns a data frame with cryptocurrency symbol, time frame, and closing price.
```{r}
price_df <- retrieve_data("BTC-USDT", "1day", "2021-01-01", "2021-12-31")
```

### Data overview
We can take a look at the head of the data frame.
```{r}
head(price_df)
```

### Plot the price data
We can plot the price data using the data frame we just retrieved.
```{r fig.width=7, fig.height=4}
plot_price(df = price_df)
```

 

### Calculate daily growth rate
This function performs calculation of daily growth rate of the price of the cryptocurrency inputted over a period of time.
We store the result as a variable for the purpose of viewing the data.
```{r}
new_price_df <- daily_growth_rate(price_df, "Close")
head(new_price_df)
```

### Calculate average daily return
```{r}
avg_daily_return(price_df$Close)
```



